---
title: "New"
date: 2022-10-14T10:09:13+02:00
draft: false
output: md_document
cover: "crane_circle.png"
description: "Test me"
---
<!-- add customURL: "https://baidu.com/" to header if you want to link to another site  -->

# Idea

Following the *KISS* principle of modeling I start with the simplest model
possible to investigate shock amplifications in the global trade network. The 
question is how shocks at the micro/sector level may trigger major global 
economic shocks. 

## Supply Chain 1

```{r supply-chain1, fig.margin=T, ref.label='supply-chain1', fig.cap = "Simple one good two country economy. A 10\\% percent shock in China will lead to a 10\\% reduction of output in the U.S. Thus, there is no shock amplification.", echo=F, fig.height=1}

# create theme
library( Rphd )
colors <- c( "#011936",
             "#942911",
             "#F49937",
             "#93B7BE" )
theme_blank <- theme( axis.text = element_blank(),
                      axis.text.x = element_blank(),
                      axis.title = element_blank(),
                      axis.ticks = element_blank(),
                      panel.background = element_rect(fill = "transparent",
                                                      colour = NA_character_), # necessary to avoid drawing panel outline
                      plot.background = element_rect(fill = "transparent",
                                                     colour = NA_character_), # necessary to avoid drawing plot outline
                      legend.background = element_rect(fill = "transparent"),
                      legend.box.background = element_rect(fill = "transparent"),
                      legend.key = element_rect(fill = "transparent" ),
                      legend.position = "none" )

# create data
g <- data.frame( "x"  = c( 1, 4 ), 
                 "y"  = c( 2, 2 ), 
                 "node_label" = c( "China", "United\nStates" )  )


ggplot( g, aes( x, y, color = node_label, label = node_label ) ) +
  geom_line( color = "black" ) +
  geom_point( size = 25 ) +
  geom_text( size = 5, color = "white" ) +
  scale_x_continuous( expand = c( 0.2, 0.2 )) +
  scale_y_continuous( expand = c( 0, 0 ) ) +
  scale_color_manual( values = colors ) +
  theme_blank
```

Let's start with the simplest trade model possible and look at a world with only
one good and two countries, let's say China and the United States, where China 
is the supplier of raw materials and the U.S. uses these materials to produce
consumption goods for U.S. citizens. In this model (see figure 
\ref{fig:supply-chain1}), shocks evolve linear (no amplification) and affect 
each country equally.

## Supply Chain 2

If we add a second good to the economy (see figure \ref{fig:supply-chain2}), 
things may change. Let's say the U.S. needs 75 of good 1 and 25 of good 2 to 
produce 100 of good 3. Assume another 10% shock hits the Chinese economy, 
however, the crisis only affects good 2. Hence, output of good 2 drops from 25 
to 15. While the total shock for China is still 10%, things changed considerably 
for the United States as output drops by 40% ($10/25=40\%$).

```{r supply-chain2, fig.margin=T, ref.label='supply-chain2', fig.cap = "Simple two good two country economy. A 10\\% percent shock in China's good 1 sector will lead to a larger reduction of output in the U.S. depending on the production input ratio. Thus, there is an amplification of the shock.", echo=F, fig.height=2}

# create data
g <- data.frame( "x"  = c( 1, 1, 4 ), 
                 "y"  = c( 3, 1, 2 ),
                 "node_label" = c( "China\nGood 1", "China\nGood 2", "United\nStates" ),
                 color = c( "China", "China", "United States" ) )

g_line1 <- data.frame( "x"  = c( 1, 4 ), 
                       "y"  = c( 1, 2 ) )

g_line2 <- data.frame( "x"  = c( 1, 4 ), 
                       "y"  = c( 3, 2 ) )

ggplot() +
  geom_line( mapping = aes( x, y ), data = g_line1, color = "black" ) +
  geom_line( mapping = aes( x, y ), data = g_line2, color = "black" ) +
  geom_point( mapping = aes( x, y, color = color ), data = g, size = 25 ) +
  geom_text( mapping = aes( x, y, label = node_label ), data = g, size = 5, color = "white" ) +
  scale_y_continuous( expand = c( 0.25, 0.25 ) ) +
  scale_x_continuous( expand = c( 0.2, 0.2 ) ) +
  scale_color_manual( values = colors ) +
  theme_blank
```

## Supply Chain 3

*Supply chain 2* is a simple example of how sector-specific shocks in one country may 
amplify. What we also see is that countries at the end of the supply chain are 
more vulnerable than countries at the beginning as they depend on many more
countries. To see this we do one more simple example of probability of default.
Let's assume at each link in figure \ref{fig:supply-chain3} has a 
probability of default of 5%. This results in the following default 
probabilities: India = $5\%$, France $\rightarrow 1-0.95^2=9.8\%$, and the U.S.
$\rightarrow 1-0.95^3=14.3\%$.

```{r supply-chain3, ref.label='supply-chain3', fig.cap = "Simple 4-player supply chain. The default probability grows with each link in the network. Thus, producers at the end of the supply chain face higher risks.", echo=F, fig.height=0.6}

# create data
g3 <- data.frame( "x"  = c( 1, 2, 3, 4 ), 
                 "y"  = c( 2, 2, 2, 2 ),
                 "node_label" = c( "China", "India", "France", "United\nStates" ) )

g_line3 <- data.frame( "x"  = c( 1, 4 ), 
                       "y"  = c( 2, 2 ) )

ggplot() +
  geom_line( mapping = aes( x, y ), data = g_line3, color = "black" ) +
  geom_point( mapping = aes( x, y, color = node_label ), data = g3, size = 13 ) +
  geom_text( mapping = aes( x, y, label = node_label ), data = g3, size = 2, color = "white" ) +
  scale_y_continuous( expand = c( 0.25, 0.25 ) ) +
  scale_x_continuous( expand = c( 0.2, 0.2 ) ) +
  scale_color_manual( values = colors ) +
  theme_blank
```

## Conclusion and what is missing

- Shocks may amplify depending on which industries and countries are affected. 
- Later stages of the supply chain bear higher risks.
- If available, good 2 can be sourced from other suppliers, hence, the shock
would be dampened. Prices might go up.
- A shock can be (temporarily) mitigated by domestic stocks.
- There will be repercussions. If the U.S. experiences a dramatic drop in 
economic output industry 2 will also be affected. Hence, the shock will also hit
China stronger than initially expected.
